 \documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{enumerate}
\usepackage{framed}
\usepackage{subfigure}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 2011 13:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

%\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
\lhead{Maths Resource} \rhead{Introduction to Probability}
\chead{Probability }
%\input{tcilatex}

\begin{document}
\section*{Probability Tutorial Sheet A}
\begin{enumerate}
    \item 
A fair coin is tossed three times. Write out the sample space S.

Write the sample points of the following events

\begin{enumerate}[(i)]
\item the event that the first toss is heads
\item the event that the second toss is heads
\item exactly two heads in a row.
\end{enumerate}


\item 
A couple has two children; the sample space is $S = \{bb, bg, gb, gg\}$ with probability 0.25 for each sample point. Find the probability p that both children are boys if it is known that: 
\begin{enumerate}[(i)]
\item at least one of the children is a boy;
\item  the older child is a boy
\end{enumerate}

\item 
Compute the probability $p$ of each event:
\begin{enumerate}[(i)]
\item An even number appears in the toss of a fair die;
\item One or more tails appear in the toss of three fair coins;
\item A blue marble appears in a random drawing of one marble from a box containing four white, three blue, and five red marbles.
\end{enumerate}

\item 
Suppose a student is selected at random from 100 students where 30 are taking mathematics, 20 are taking computer science, and 10 are taking mathematics and computer science. Find the probability p that the student is taking mathematics or computer science.
\item 
A lot contains 13 items of which 4 are defective. Three items are drawn at random from the lot one after the other. Find the probability p that all three are nondefective.

\end{enumerate}
\end{document}


\end{document}
