\documentclass[]{report}

\voffset=-1.5cm
\oddsidemargin=0.0cm
\textwidth = 480pt

\usepackage{framed}
\usepackage{subfiles}
\usepackage{graphics}
\usepackage{newlfont}
\usepackage{eurosym}
\usepackage{amsmath,amsthm,amsfonts}
\usepackage{amsmath}
\usepackage{color}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\begin{document}

	
	%------------------------------------- %
\section{Computer Output}
Statistical Procedures were performed using a statistical programming language called $R$.
A brief description of each procedure is provided. For each procedures, identify the null and alternative hypotheses, the $p-$value, and your conclusion for this test.


\begin{itemize}
	\item If the $p-$value is less than 0.05 : reject the null hypothesis.
	\item If the $p-$value is greater than 0.05 : fail to reject the null hypothesis.
\end{itemize}
% prop.test
% Shapiro Wilk
% Grubb's
% var test
\subsection*{Test 1. Single Sample Test for Proportions}
\begin{itemize}
	\item Sample size ($n$) = 500
	\item Number of successes ($x$) = 280
	\item Expected value under null hypothesis (Usually $\pi$, but here as $p$)
\end{itemize}
\begin{framed}
	\begin{verbatim}
	> prop.test(x=280,n=500,p=0.60)
	
	1-sample proportions test with continuity correction
	
	data:  280 out of 500, null probability 0.6
	X-squared = 3.1688, df = 1, p-value = 0.07506
	alternative hypothesis: true p is not equal to 0.6
	95 percent confidence interval:
	0.5151941 0.6038700
	sample estimates:
	p 
	0.56 
	> 
	\end{verbatim}
\end{framed}
\newpage
	\subsection*{Question 11 - Shapiro-Wilk Test}
	Interpret the output from the three Shapiro-Wilk tests. What is the null and alternative hypotheses? State your conclusion for each of the three tests.
	\begin{framed}
		\begin{verbatim}
		> shapiro.test(X)
		
		Shapiro-Wilk normality test
		
		data:  X
		W = 0.9001, p-value = 0.113
		>
		\end{verbatim}
	\end{framed}
	\begin{framed}
		\begin{verbatim}
		> shapiro.test(Y)
		
		Shapiro-Wilk normality test
		
		data:  Y 
		W = 0.8073, p-value = 0.006145
		>
		\end{verbatim}
	\end{framed}
	\begin{framed}
		\begin{verbatim}
		> shapiro.test(Z)
		
		Shapiro-Wilk normality test
		
		data:  Z
		W = 0.9292, p-value = 0.372
		\end{verbatim}
	\end{framed}

\subsection*{Test 2. F Test for equality of variance}
\begin{itemize}
	\item In this procedure, we determine whether or not two \textit{\textbf{populations}} have the same variance.
	\item The assumption of equal variance of two populations underpins several inference procedures. This assumption is tested by comparing the variance of samples taken from both populations.
	\item The null and alternative hypotheses are as follows:
	\[ H_0: \sigma^2_1 = \sigma^2_2 \]
	\[ H_1: \sigma^2_1 \neq \sigma^2_2 \]
\end{itemize}
\begin{framed}
	\begin{verbatim}
	> var.test(X,Y)
	
	F test to compare two variances
	
	data:  X and Y
	F = 2.5122, num df = 9, denom df = 9, p-value = 0.1862
	alternative hypothesis: true ratio of variances
	is not equal to 1
	95 percent confidence interval:
	0.6239986 10.1141624
	sample estimates:
	ratio of variances 
	2.512215 
	\end{verbatim}
\end{framed}

\subsection*{Test 3. Shapiro Wilk's Test for Normality}
\begin{itemize}
	\item We will often be required to determine whether or not a data set is normally distributed.
	This assumption underpins many statistical models.
	\item The null hypothesis is that the data set is normally distributed.
	\item The alternative hypothesis is that the data set is not normally distributed.
	\item One procedure for testing these hypotheses is the Shapiro-Wilk test, implemented in \texttt{R} using the command \texttt{shapiro.test()}.
\end{itemize}
\begin{framed}
	\begin{verbatim}
	> shapiro.test(X)
	
	Shapiro-Wilk normality test
	
	data:  X
	W = 0.9849, p-value = 0.1012
	
	
	\end{verbatim}
\end{framed}

\end{document}	
