\documentclass[]{report}

\voffset=-1.5cm
\oddsidemargin=0.0cm
\textwidth = 480pt

\usepackage{framed}
\usepackage{subfiles}
\usepackage{graphics}
\usepackage{newlfont}
\usepackage{eurosym}
\usepackage{amsmath,amsthm,amsfonts}
\usepackage{amsmath}
\usepackage{color}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\begin{document}
%-------------------------------------------------%
\begin{enumerate}
\item 
The strength of dosage of a plant growth enhancement chemical 
is often measured by the proportion of plants that grow faster. 
A particular dosage of the chemical is fed to 115 plants of these plants, 94 actually show faster growth. 

\begin{enumerate}       
\item Calculate a point estimate $\hat{p}$ for the proportion of plants that grow faster due to the  dosage. 3 

\item What is the standard error of the estimate in (i)? 

\item Find a 95\% confidence interval for p.  

\item What size sample is required to give the estimate in (iii) to within $\pm 1\%$.  

\item Carry out a testing procedure to investigate the claim that the chemical is 90\% effective.

\end{enumerate}




%------------------------------------------------------------------------------------------------------------------------------------------------%

\item
In the British General Election, from a random sample of 900 voters, 468 people said they would vote for the Labour Party.  
\begin{itemize}
	\item[(i)] You are required to construct a 95\% Confidence Interval based on survey data for the proportion of people who will vote for the Labour Party in the election.
	% (2 marks)
	
\item[(ii)]If the leadership of the Labour Party wanted the error in the survey to be $\pm 1\%$ at a 95\% Confidence Interval, how many people should they interview
	
\end{itemize}

\begin{itemize}
	\item[(i)]Using the survey results as a prior estimate of the proportion of people supporting the Labour Party
	% (4 marks)
	\item[(ii)]If no prior information were available, how many people would need to be surveyed?
	%(5 marks)
\item (c)The Labour Party claims that a majority of the British population (p = 50\%) support them.  Based on the survey results, is there any evidence to reject this hypothesis at the 1\% level of significance? 
%(9 marks)

\end{itemize}
%-----------------%


\item 
In the past, 18\% of shoppers have bought a particular brand of breakfast cereal.
After an advertising campaign, a random sample of 220 shoppers is taken and 55 of the sample have bought this brand of cereal.

Write down the null and the alternative hypothesis for this problem, and state whether it is a one tailed or two tailed test

The conventional treatment for a disease has been shown to be effective in
80\% of all cases. A new drug is being promoted by a pharmaceutical
company; the Department of Health wishes to test whether the new treatment
is more effective than the conventional treatment.

Write down the null and the alternative hypothesis for this problem, and state whether it is a one tailed or two tailed test




\item 
Two time-sharing systems are compared according to their response
time to an editing command. 
\begin{itemize} 
\item The mean response time of 100 requests
submitted to system 1 was measured to be 600 milliseconds with a
known standard deviation of 20 milliseconds. \item  The mean response time
of 100 requests on system 2 was 592 milliseconds with a known
standard deviation of 23 milliseconds. \end{itemize} 
\begin{enumerate}[(i)]
\item sing a significance level of $5\%$,
test the hypothesis that system 2 provides a faster response time than
system 1.  Clearly state your null and alternative hypotheses and your
conclusion.
\end{enumerate}
\end{document}
