\section{Spring 2007 /2008}
A company’s annual earnings are known to be normally distributed with a mean of €15 million and a standard deviation of €2 million. Determine the probability that in 2008 the company earns:

\begin{itemize}
	\item[(i)]           less than €15 million  ,
	\item[(ii)]          greater than €17 million  ,
	\item[(iii)]         between €13 and €17 million  .
\end{itemize}
Solution 

X is the company’s earnings in a given year, in millions.

i)  Find  

Remark

The mean is  €15 million. By definition 50% of the random variable values are less than the mean of the normal distribution.

But let’s do this question using a procedure that we can use for all questions.

Step 1
First , we find the z-value that corresponds to x = 15 
(remember   and   )


Therefore we can say   =  


Step 2

The Murdoch Barnes tables are tabulated to give   for some value  . 

We can compute   using the complement rule

= 1 -  

From the tables   = 0.500

Therefore    = 1 - 0.500 = 0.500

If    = 0.5 , necessarily   = 0.5     [    Answer    ] 

%======================================================================%


ii)  Find  

First , we find the z-value that corresponds to x = 17 
(remember   and   )


Therefore we can say   =  

The Murdoch Barnes tables are tabulated to give   for some value  . 
We can evaluate   as 0.1587

If    = 0.1587 , necessarily   = 0.1587     [    Answer    ] 

%======================================================================%


(iii)  Probability of being between €13 and €17 million .



Easier to compute the complement event  - being either too low or too high.

1)	 Too high

=? 

Answer from part (ii) 0.1587

2)	Too low

= ?

First find the z value for x = 13



Therefore we can say   =  

Use the symmetry rule to evaluate  

=  
From part (ii) we found   =0.1587

Therefore   = 0.1587

Therefore   = 0.1587

\begin{framed}
	Remark : 
	
	We have a chain of equivalent statements.
	
	If A = B , B = C, and C=D, then A = D 
\end{framed} 


3)	Putting it all together

Too Low: probability is 0.1587

Too High: probability is also 0.1587

Outside interval : "Too low" or "Too high" = 0.3174

Inside interval : 1 - 0.3174 = 0.6826

= 0.6826     [    Answer    ] 

%======================================================================%

\section{ Spring 2006 /2007 }

The duration of Mr. Jones’ morning commute to work is normally distributed with a mean of 35 minutes and a standard deviation of 5 minutes. Determine the probability that Mr. Jones’ commute is

\begin{itemize}
	\item[(i)]    less than 32 minutes,
	\item[(ii)]   greater than 39 minutes,
	\item[(iii)]   between 33 and 38 minutes.
\end{itemize}

\noindent \t{Solution}

$X$ is the normal random variable describing travelling times

i)   =? 
First , we find the z-value that corresponds to x = 32 
(remember   and   )


Therefore we can say    =  

We can evaluate    using the symmetry rule

=  

From Murdoch Barnes table 3         = 0.2743

Therefore    = 0.2743         [  Answer ] 


%======================================================================%

ii)   =? 
First , we find the z-value that corresponds to x = 39 (remember   and   )



Therefore we can say    =  

From Murdoch Barnes table 3      = 0.2119   
Therefore    = 0.2119            [  Answer ] 


%======================================================================%

Part iii) 

Probability of being between 33 and 38 minutes 



Easier to compute the complement event  - being either too low or too high.

1)	Too high

=? 
First, we find the z-value that corresponds to x = 38  (remember  and   )



Therefore we can say    =  

From Murdoch Barnes table 3      = 0.2743  
Therefore    = 0.2743         


%======================================================================% 
2)	 Too low

=? 
First, we find the z-value that corresponds to x = 33  (remember  and   )


Therefore we can say    =  

We can evaluate    using the symmetry rule

=  

From Murdoch Barnes table 3         = 0.3446

Therefore    = 0.3446         


%======================================================================%

3)	Putting it all together

\begin{description}    
	\item[Too Low:] probability is 0.2753
	\item[Too High:] probability is also 0.3446
\end{description}

\[    \mbox{Outside interval} : \mbox{"Too low" + "Too high"} = 0.6199\]

Inside interval : 1 - 0.6199 = 0.3801


%======================================================================%    

= 0.3801     [    Answer    ] 


%=======================================================================%



	%-----------------------------------------------------%
\end{document}	
