	2009/GD5/Q8
			
			8. Monthly magazines are often directed at special interests of their readers, such as the countryside, wildlife, sport, motor cars. The marketing manager for one of these magazines is trying to encourage advertisers to place advertisements in her magazine. She therefore wishes to collect information on the number and types of people who read the magazine, regularly or occasionally, and their interests.
			
			(i) Paying particular attention to the problems of constructing a sampling frame, undercoverage, non-response and likely requirements of advertisers, recommend a method
			for selecting a sample from the readership. (10)
			
			(ii) Comment on the types of information the manager should aim to collect, in addition to standard questions about name, address, age, occupation, etc. (5)
			
			(iii) How could the frame be used, and how could the results of the exercise be kept up to date, to satisfy the likely needs of the advertisers? (5)
			
	
			
		
		
			Q1
			
			A multinational corporation (MNC) has two manufacturing facilities – one in Limerick, the other in Texas, both producing identical products and employing roughly the same number of ‘direct’ employees, i.e. directly involved in manufacturing.  The Operations Director randomly selected 9 weeks from the previous years production figures.  Each of the weeks chosen, employees worked 5 full days and no overtime.  The production figures for each facility is as follows (units in thousands)
			
			
			IrelandTexas
			13.83.7
			23.93.8
			34.03.6
			43.73.3
			53.63.4
			64.13.5
			73.93.6
			84.03.7
			94.13.4
			
			
			(a)You are required to construct a box plot for each factory’s output and to comment on the salient features of each plot.  Is there evidence from the box plots to reject the hypothesis that there is no difference in the production figures between the two facilities?  Use the box plot to justify your comments. (8 marks)
			
			(b)Compare and contrast the Mean and the Median as measures of location
			(2 marks)
			
			(c)Two independent resistors are located in a simple circuit as shown below.  The probability that A and B works is 0.8 and 0.7 respectively.  You are required to calculate the probability that the signal will travel from x to y.  If the two resistors were arranged in series, what difference would this make to the probability of the signal reaching y?
			(10 marks)
			
			
			
			
			
			
			
			
			(c)A random sample of 100 parts (from (a) above) revealed that for 4 of those parts, the critical diameter measurements were outside spec.  You are requested to construct a 95% confidence interval for the proportion defective.
			
			If the company wished to estimate the defective rate to within + or - 2% with 99% confidence, how big a sample would need to be undertaken to provide the relevant information?
			(8 marks)
			
			
			
			
			Q3
			The data from Question 1 (reproduced below) should be used to answer the following question.
			
			IrelandTexas
			13.83.7
			23.93.8
			34.03.6
			43.73.3
			53.63.4
			64.13.5
			73.93.6
			84.03.7
			94.13.4
			
			
			
			IrelandTexas
			Sample Mean3.903.56
			Standard Deviation0.173x
			
			(a)Fill in the missing section from the above table(2 marks)
			(b)Does the data provide sufficient evidence to support the hypothesis that the populations are of equal variances?  Use a 5% level of significance and indicate clearly all calculations made. (9 marks)
			(c)You are required to test the hypothesis that there is no statistical difference between the number of units produced at each plant.  Use a test with a 5% probability of a Type 1 error.(9 marks)
			
			
			
			
			
			.
			
			
			
			
			
			%-------------------------------------------------------------------------------%
			Q1
			
			A telecommunications company has two servers from different suppliers. The Operations Director randomly selected 9 months from the previous year’s figures.  The down time figures for each server is as follows (down time per month in hours)
			
			
			Server 1Server 2
			15.35.4
			25.45.5
			35.56.1
			45.25.0
			55.15.1
			65.65.2
			75.45.3
			85.55.4
			95.65.9
			
			
			(a)You are required to construct a box plot for each server’s output and to comment on the salient features of each plot.  Is there evidence from the box plots to reject the hypothesis that there is no difference in the down time between the two servers?  Use the box plot to justify your comments. (8 marks)
			
			(b)Compare and contrast the Mean and the Median as measures of location
			(2 marks)
			
			(c)Two independent resistors are located in a simple circuit as shown below.  You are required to calculate the probability that the signal will travel from x to y.  Resistor A has a mean time of 20 hours to failure and Resistor B a mean time of 40 hours.  Assume that the respective failure rates follow an exponential distribution.  What is the probability that signal integrity will be maintained between x and y for 30 or more hours?
			(10 marks)
			
			
	
			
			
			
			Q3
			Two facilities, one in Limerick and the other in Galway produce identical products on similar lines.  The production manager randomly selected 9 weeks from the previous year’s production.  The number of units produced in each facility was recorded in thousands as follows:
			
			LimerickGalway
			13.83.7
			23.93.8
			34.03.6
			43.73.3
			53.63.4
			64.13.5
			73.93.6
			84.03.7
			94.13.4
			
			
			
			LimerickGalway
			Sample Mean3.903.56
			Standard Deviation0.173x
			
			(a)Fill in the missing section from the above table(2 marks)
			(b)Does the data provide sufficient evidence to support the hypothesis that the populations are of equal variances?  Use a 5% level of significance and indicate clearly all calculations made. (9 marks)
			(c)You are required to test the hypothesis that there is no statistical difference between the number of units produced at each plant.  Use a test with a 5% probability of a Type 1 error.(9 marks)
			
			
			
			
			MA4704 Technological Maths 4 
			
			Q1
			A multinational company has two sub suppliers, one in Taiwan and the other in mainland China.  Both plants have similar production facilities and are dedicated exclusively to supplying a company based in Ireland with components.
			The number of defects per shipment is recorded as follows:
			
			SubS 116181922222528282831332723
			SubS 222232527272830323335363838
			
			(a)You are required to construct a box plot for each plant’s output and to comment on the salient features of each plot.  Is there evidence from the box plots to reject the hypothesis that there is no difference in the defect figures between the two facilities?  Use the box plot to justify your comments.
			(8 marks)
			
			(b)Compare and contrast the Mean and the Median as measures of location
			(2 marks)
			
			(c)The mean of three numbers: w, y, z is x
			
			(i) Express x in terms of w, y, z
			(ii)  If a and b are constants express the means of 
			aw + b;   ay + b;   az + b
			in terms of  
			(10 marks)
			
			
			
			%---------------------------------------------------%
			%
			%(b) (i) P(EF) denotes the conditional probability of “E given F”. 
			%Write down an equation to express the relationship between 
			%P(F), P(EF) and P ( E  F)
			%(ii) E and F are events such that   P(EF) = ½ ,   P(EF) =  ⅓ 
			%and P ( E  F) = 1/7
			%Find P(E F)
			%(iii) Are the events E and F in part (ii) independent? Give a reason for your answer.(7 marks)
			%
			
			
	
			\section{Question 5} 
			
			The National Roads Authority is studying the relationship between the number of bidders on a Motorway project and the winning (lowest) bid for the project.  Of particular interest is whether the number of bidders increases or decreases with the amount of the winning bid.
			
			Observation number Number of Bidders (x)Winning Bids
			(y)
			154.0
			286.9
			343.9
			497.8
			532.7
			666.1
			744.4
			876.2
			
			%%\sumxy =1932 \sumx2 =2116 \sumx =46\sumy =  42\sumy2 = 1764 
			
			
			(a) You are required 
			(i)To draw a Scatter Gram and comment on its features
			(ii) Find the regression equation and plot the regression equation on the scattergram
			(iii) Use a 5% level of significance to test the hypothesis that R correlation coefficient equals zero.  Interpret your answer.
			(12 marks)
			
			%-----------------------------------------%
			
			(b) The above data was entered into Minitab and the following output was generated:
			You are requested to fill in the blanks in the following table:
			Analysis of Variance
			
			Source            DF          SS          MS         F        P
			Regression              x         20.160      20.160   x         0.000
			Residual Error         x        xx              xxx
			Total                     x         21.460
			
			
			Observation    Number of BiddersWinning BidFitted valueResidual
			28        6.9       x      x
			
			(8 marks)
			
			
			
			
			Question 3
			(a)Suppose 40\% of employees in a large company favour unionisation.  A poll of 10 employees in this company is taken.  
			
			(i)What is the probability that 4 or more employees polled favour unionisation? 
			(ii)What is the probability that less than 2 employees polled favour unionisation?
			(iii)What is the probability that exactly 5 employees polled favour unionisation?
			(iv)What is the mean and variance for this distribution?
			(9 marks)
			
			
			
			%--------------------------------------------------------------%
			(c)Telephone calls coming in to a busy switchboard follow a Poisson distribution with 3 calls expected in a one minute period.  The switchboard operator can answer at most 3 calls in a one minute period; the fourth and succeeding calls receive a busy signal.
			
			(i)   Find the probability of receiving a busy signal.
			(ii)   The switchboard operator leaves the switchboard unattended for 2 minutes.  What is the probability that exactly 1 call will be missed during that 2 minute period?
			(6 marks)
			
			(d)In what circumstances can the Poisson distribution be used to approximate the Binomial distribution?
			(2 marks)
			
			
			Q4
			
			
			(a)  Four  per cent of PCB boards purchased over the Internet from the Far East have some defect.  From a large consignment of boards, 50 are chosen at random.  What is the probability that:
			(i)3 or more boards have some defect?
			(ii)Exactly 2 boards are defective?
			(iii)Less than 3 boards are defective?
			(iv)If more than 5 boards from the 50 were defective what action would you take? (justify)
			
			(b) Flaws occur in a hard wood timbers  at the rate of 1.5 per linear  metre section.  Calculate the probability that:
			(i)3 or more flaws will occur in a 3  metre length 
			(ii)Exactly 4 flaws will occur in a 10 metre length
			(iii)8 or less flaws will occur in a 6  metre length 
			
			(c)There is a constant probability of 0.05  that the power supply in telecoms network will not start.  You are requested to calculate the probability that the power supply will fail the 5th time it is activated.
			
			%==================================================================%
			\newpage
			
