\documentclass[]{report}

\voffset=-1.5cm
\oddsidemargin=0.0cm
\textwidth = 480pt

\usepackage{framed}
\usepackage{subfiles}
\usepackage{graphics}
\usepackage{newlfont}
\usepackage{eurosym}
\usepackage{enumerate}
\usepackage{amsmath,amsthm,amsfonts}
\usepackage{amsmath}
\usepackage{color}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\begin{document}




%============================================%
% PMS Spring 2008 Question 4 - Probability
\section*{Question 1}
Consider Two events A, B such that

\begin{itemize}
\item P(A) = 0.3
\item P(A $\cap B$) = 0.1
\end{itemize}

Find the minimum possible value of $P(A|B)$

\[ P(A|B) = \frac{P(A \cup B) }{P(B)}\]

\begin{itemize}
\item $P(A \cup B) Maximum = 1$
\item $P(A \cup B) Minimum = 0.3$
\end{itemize}

\subsection*{Minimum}

\[ P(A \cup B) = P(A) + P(B) - P(A \cap B)\]
\[ 0.3 = 0.3 + P(B) - 0.1 \]
\[ P(B) = 0.1\] 

\subsection*{Maximum}

\[ P(A \cup B) = P(A) + P(B) - P(A \cap B)\]
\[ 1 = 0.3 + P(B) - 0.1 \]
\[P(B) = 0.8\]

\[ P(A|B)_{MIN} = \frac{P(A \cup B) }{P(B)} = \frac{0.1}{0.8} = 0.125 \]
\[ P(A|B)_{MAX} = \frac{P(A \cup B) }{P(B)} = \frac{0.1}{0.1} = 1 \]

%=================================================================================%

\subsection*{Question 3: Defective Electronics}
Suppose an electronics assembly subcontractor receives resistors from only two suppliers: A and B

\begin{itemize}
\item Suppose we are told that Supplier A supplies 80\% of the resistors

\end{itemize}

\begin{framed}
\begin{itemize}
\item Supplier A supplies 80\% of the resistors
\item \textit{Probability that a randomly chosen resistor comes from A is 80 \%} : \textit{P(A) = 0.80 }
\item Supplier B supplies 20\% of the resistors
\item \textit{Probability that a randomly chosen resistor comes from B is therefore 20\%} : \textit{P(B) = 0.20}
\end{itemize}
\end{framed}



\begin{itemize}
\item We are giving information about the rate of faulty components from each supplier. \\(Faulty : resistor fails some 
\item 1\% of the resistors supplied by A are faulty

\item 3\% of the resistors supplied by B are faulty 
\vspace{1cm}
\end{itemize}

\begin{itemize}
\item We are giving information about the rate of faulty components from each supplier. \\(Faulty : resistor fails some quality test)
\item  \textit{P(F) probability that randomly selecting compoent is faulty}
\item 1\% of the resistors supplied by A are faulty.
\item\textit{ We write this as $P(F|A) =0.01$}
\item 3\% of the resistors supplied by B are faulty 
\item \textit{We write this as $P(F|B) =0.03$}
\end{itemize}
\newpage



\section{Question 1}
Events  (Important the event names are explained)

\begin{itemize}
\item F: Student plays footballP(F) = 50%
\item S: Student does SwimmingP(S) = 20%
\item F and S:            Student takes part in both swimming and football  
\end{itemize}

P(S and F) = 15%

Find P (F or S)
Use addition rule

\begin{eqnarray}P (F or S)  &=  P(F) + P(S) – P( Fand S)\\
&=  50% + 20 % - 15%\\
&=   55%\\
\end{eqnarray}

(We subtract 15\% to stop the “boths” getting counted twice)

Probability of playing neither
This is the complement event of playing one or both sports.
\[P(Neither) = 1 –  P( F or S)  = 45\%\]

\subsection{Question 2} 
2 components A and B.
P(A) = event that A is workingP(A) = 0.98
P(B) = event that B is workingP(B) = 0.95
P(A and B) = event that both A and B are working = P(A) x P(B) = 0.98 x 0.95 = 0.931

\subsection{Question 3}
Lots of useless information.
Complement event of at least one working is that they are both broken.

Answer  100 – 4\% = 96%

\subsection{Question 4}



Events 
\begin{description}
\item[A] components from supplier A  P (A) = 0.8 
\item[B] components from supplier B  P (B) = 0.2 
\item[F] resistor fails test
\end{description}

\begin{verbatim}
1\% Probability of a Failure given that component is from Supplier A.      P(F|A) = 0.01
3\% Probability of a Failure given that component is from Supplier B.      P(F|B) = 0.03
\end{verbatim}
Probability of flaw : P(F)
Failed resistors either come from A or B
\[P( F) =  P ( F \mbox{ and } A)  +  P( F \mbox{ and } B)\]
Use conditional Probability  rule
\[P(F) = P(F|A)\times P(A)  + P(F|B)\times P(B)\]

\[P(F)  =  ( 0.01 x 0.8 ) + ( 0.03 x 0.2) = (0.008) + (0.06) = 0.014\]
Answer 1.4%

Part ii
Given that a component failed, what was the probability of coming from A
P(A|F) 

P(A|F) = P(A and F)  / P(F)We found P(A and F) earlier ; 0.008

\[P(A|F) = 0.008/0.014 =  0.57\][answer : 57\%]

%========================================================================%
\subsection{Basic Probability Questions}

Suppose a pair of fair dice is thrown. 
\begin{itemize}
\item[(a)] What is the probability of getting a sum of 9 from two throws of a dice
\end{itemize}
Find the probability that the sum is 10 or greater if
\begin{itemize}
\item[(b)] a 5 appears on the first die, 
\item[(c)] a 5 appears on at least one of the dice.
\end{itemize}

%========================================================================%
\subsection{Basic Probability Questions}
Tickets numbered 1 to 20 are mixed up and then a ticket is drawn at random. What is the probability that the ticket drawn has a number which is a multiple of 3 or 5



%========================================================================%
\subsection{Exercise : Probability of Two Dice Rolls}
A pair of dice is thrown. Let X denote the minimum of the two numbers which occur.
Find the distributions and expected value of X.

\newpage
%========================================================================%
\subsection{Question 6}

\begin{verbatim}
A = coming from supplier AP(A) = 50\%
B = coming from supplier BP(B) = 30\%
C = coming from supplier CP( C)= 20\%

D = being defective

Given P(D|A) = 0.01P(D|B) = 0.03P(D|C) = 0.04


P(D) = P( D and A) + P( D and B) + P(D and C)
= P(D|A).P(A) +  P(D|B).P(B) + P(D|C).P(C)
= (0.01 X 0.5)  + (0.03 X 0.30) + (0.04 X 0.20)
= 0.005 + 0.009 +  0.008
= 0.022 [I.E. 2.2%]


P(B|D) = P(B and D) / P(D)  
= 0.009/0.022 =  0.409[41%]
\end{verbatim}
% Question 5 in lectures
% Answer P(D) =0.0395 (3.95%)
% P(C|D) = 0.0506(5.06%)



\newpage
\textbf{Question 1:}
\begin{itemize}
\item What is the probability that a randomly selected resistor fails the final test?

\item In mathematical terms, compute P(F) 
\end{itemize}


\textbf{Law of Total Probability:}
\begin{itemize}
\item Faulty Resistors are either from Supplier A or Supplier B.
\vspace{0.3cm} 
\item \textit{Resistors MUST come from one of the two suppliers.}
\item \textit{A and B are mutually exclusive.}
\end{itemize}
\vspace{0.3cm} 
\[ P(F) = P(F \mbox{ and } A) + P(F \mbox{ and } B) \]






\section*{Question 11 - Summary Statistics}

The following data give the marks of 10 students in a test (out of 20 marks). Calculate
\begin{itemize}   
\item[(a.)] the median    
\item[(b.)] the mean     
\item[(c.)] the range    
\item[(d.)] the standard deviation 
\item[(e.)] The Inter-Quartile Range
\end{itemize}

\[12, 17, 7, 11, 18, 6, 14, 15, 11, 9.\]




\textbf{Probability Table} \\ \bigskip
\begin{tabular}{|c|c|c||c|}
\hline  &  \phantom{sp} Europe \phantom{sp} & \phantom{sp} Outside \phantom{sp} & \phantom{sp} Total\phantom{sp}  \\ 
\hline On Time  & 48.82\% & 30.00\% & 78.82\% \\ 
\hline Late & 14.12\% & 7.06\% &  21.18\% \\ \hline
\hline Total  & 62.94\% & 30.06\% & 100.00\% \\ 
\hline 
\end{tabular} 



Using the probability table answer the following questions. \\
\bigskip
For a randomly chosen flight departing from this airport, what is the probability that it: 
\begin{itemize}
\item[(a)] Departs on time? 
\item[(b)] Departs with a delay and is a flight outside Europe? 

\item[(c)] Departs on time or is a flight outside Europe? 
\item[(d)] Departs on time, given that you know it is a flight within Europe? 

\item[(e)] Is a flight within Europe, given that you know that it departs on time?
\end{itemize}





\section*{Question 14 - Urn Question}



\section*{Discrete Random Variables}
\begin{enumerate}







\end{document}
