\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{multicol}
\usepackage{framed}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode"CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 201113:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
\lhead{MA4603} \rhead{Week 3} \chead{Science Maths 3 (Statistics)} %\input{tcilatex}
%opening
%\title{MA4413 }
%\author{Tutorial Sheet for }

\begin{document}

\newpage
2.	A die is rolled until a number divisible by 3 is obtained. Calculate the probability that
i)	the die is rolled exactly once.
ii)	the die is rolled exactly five times.
iii)	the number of rolls is even.


3.	A die is thrown 720 times.
a)	What is the distribution of the number of sixes obtained?

b) Using an appropriate approximation, estimate the probability that
i) exactly 120 sixes are obtained.
ii) between 115 and 127 (inclusively) sixes are obtained.



	
	
	
\begin{enumerate}	
	
	%--------------------------------------------------%	
	\item In the British national lottery 6 numbers are chosen without replacement from 49. Calculate the probability of 
	i)	winning the jackpot (choosing all 6 numbers correctly)
	ii)	winning the smallest prize (choosing 3 of the 6 numbers correctly)
	iii)	choosing at least one of the numbers correctly.
	%--------------------------------------------------%	
	
	\item	I obtain a hand of 13 cards. Calculate the probability of
	\begin{enumerate}[(i)]
		\item obtaining 2 aces.
		\item obtaining 2 aces and 2 kings.
		\item obtaining 2 aces or 2 kings.	
	\end{enumerate}
	
	
	\item A computer chooses a number at random n times from the set {1, 2, 3, 4, 5} (with replacement). Let S denote the sum of the numbers chosen. Show that
	E(S) = 3n and Var(S) = 2n.
	
	%\item	Let Y=aX+b. Prove that i) E(Y)=aE(X)+b, ii) Var(Y)=a2Var(X).
	
	
	
	\item	The probabilities with which Liverpool win, draw or lose a premier league match are 0.5, 0.3 and 0.2, respectively. Calculate the probability that in 8 matches
	\begin{enumerate}[(i)]
		\item 	Liverpool lose 2 matches.
		\item	Liverpool win 5 matches and draw 2.
	\end{enumerate}
	
	
	\item	A die is thrown until either a six is obtained or five rolls are done (a truncated geometric distribution). Let X be the number of rolls.
	\begin{enumerate}[(i)]
		\item 	Define the cumulative distribution function of X.
		\item	Find the median of X.
	\end{enumerate}	
	

	
	
	

\end{enumerate}

	%=====================================%
	\subsection*{Question 1 Part A}
	
	\noindent \textbf{Useful:} Binomial Probability Tree 
	\begin{itemize}
		\item All possible Outcomes:
		$\{ (HHH), (HHT), (HTH), (HTT) , (THH), (THT), (TTH),(TTT)\} $
		
		
		
		\item ``More Heads than Tails" means 2 or 3 Heads. Sample space from above written in terms of numbers f Heads: $\{ (3), (2), (2), (1), (2),(1),(1),(0)\} $
		
		\[ \Pr(\mbox{More Heads than Tails} = \Pr(\mbox{2 Heads}) + \Pr(\mbox{3 Heads}) = 3/8 + 1/8 \]
		
		\item $ \Pr(\mbox{2 Heads}) = 3/8 $
		
	\end{itemize}
	
	
	

	%=====================================%
	\subsection*{Question 1 Part C}
	Compute the probability $p$ of each event:
	\begin{itemize}
		\item[(i)] An even number appears in the toss of a fair die,
		\\
		Sample Space: $\{1,2,3,4,5,6\}$
		\\
		Relevant Sample Points : $\{2,4,6\}$
		\\ P(Even) = 0.5
		\\ \smallskip
		\item[(ii)] One or more tails appear in the toss of three fair coins,
		\\ (Based on Previous)
		\\ 7 of the 8 Sample Points in the Sample Space have a Tail
		\\ smallskip
		\item[(iii)] A blue marble appears in a random drawing of one marble from a box containing four white, three blue, and five red marbles.
		\\ P(Blue) = 3/12 = 0.25
	\end{itemize}
	
	
	
	

\end{document}
