
%--------------------------------------------------------------------------------------%
\begin{frame}
\frametitle{Example 1: Difference in Means (a) }
Two sets of patients are given courses of treatment under two different drugs. The benefits
derived from each drug can be stated numerically in terms of the recovery times. There are 40 patients in treatment group 1 (i.e. Drug 1), and 45 patients in treatment group 2 (i.e. Drug 2). The mean recovery time and standard deviations are as follows:
\begin{itemize}
\item Drug 1:  $n_1$ = 40 , $\bar{x}_1$ = 3.3 days and $s_1 = 1.524$
\item Drug 2:  $n_2$ = 45 , $\bar{x}_2$ = 4.3 days and $s_2 = 1.951 $
\end{itemize}
\end{frame}

%-------------------------------------------------------------------------------------------%
\begin{frame}
\frametitle{Example 1: Difference in Means (b) }
\begin{itemize}
\item The first step in hypothesis testing is to specify the null hypothesis and an alternative hypothesis.
\item When testing differences between mean recovery times, the null hypothesis is that the two population means are equal.
\item That is, the null hypothesis is:\\
$H_0: \mu_1 = \mu_2$ ( The population means are equal)\\
$H_1: \mu_1 \neq \mu_2$ (The population means are different)
\end{itemize}



(Remark: Two Tailed Test, therefore $k = 2$, and $\alpha = 0.05$)
\end{frame}

%-------------------------------------------------------------------------------------------%
\begin{frame}
\frametitle{Example 1: Difference in Means (c) }
\begin{itemize}
\item The observed difference in means is 1 day.
\item The relevant formula for the standard error is
\[ S.E(\bar{x}_1 - \bar{x}_2) = \sqrt{{s^2_1\over n_1}+{s^2_2 \over n_2}} \]
\item  \[ S.E(\bar{x}_1 - \bar{x}_2) = \sqrt{{(1.524)^2 \over 40}+{(1.951)^2 \over 45}}   \]
\item  \[ S.E(\bar{x}_1 - \bar{x}_2) = 0.377\mbox{ days}\]
\end{itemize}
\end{frame}
%-------------------------------------------------------------------------------------------%
\begin{frame}
\frametitle{Example 1: Difference in Means (d) }
\begin{itemize}
\item The Test statistic is therefore
\[ TS = {\mbox{observed} - \mbox{null} \over \mbox{Std. Error}}  = {1 - 0 \over 0.377 } = 2.65 \]
\item Two Tailed Test, therefore $k = 2$, and $\alpha = 0.05$. Also two large samples. The CV is 1.96.
\end{itemize}
\end{frame}


%-------------------------------------------------------------------------------------------%
\begin{frame}
\frametitle{Example 1: Difference in Means (e) }
\textbf{Decision Rule}
\[ |TS| > CV ?  \]
\begin{itemize}
\item If Yes: Reject the null Hypothesis
\item If No : Fail to reject the Null Hypothesis
\end{itemize}
$|2.65|$ is greater than 1.96. We reject the null hypothesis. There is a significant difference in the effectiveness of the two drug treatments.
\end{frame}



%--------------------------------------------------------------------------%

\begin{frame}
\frametitle{Two Small Samples Case}
\begin{itemize}
\item Previously we have looked at large samples, now we will consider small samples.
\item (For the sake of clarity, I will not use small samples that have a combined sample size of greater than 30.
\item Additionally we require the assumption that both samples have equal variance. This assumption \textbf{must} be tested with another formal hypothesis test. We will revisit this later, and in the mean time, assume that the assumption of equal variance holds.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Two Small Samples Case}
\begin{itemize}
\item The key differences between the large sample case and the small sample cases arise in the following steps.
    \begin{itemize}
    \item The standard error is computed in a different way (see next slide).
    \item The degrees of freedom used to compute the critical value is $(n_X-1) + (n_Y - 1)$) or equivalently ($n_X + n_Y - 2$).
    \item Also - a formal test of equality of variances is required beforehand (End of Year Exam)
    \end{itemize}
\end{itemize}
\end{frame}
\begin{frame}
\frametitle{Two Small Samples Case: Standard Error}
Computing the standard error requires a two step calculation. From the formulae, we have the two equations below. The first term $s_p^2$ is called the \textbf{\textit{pooled variance}} of the combined samples.
\begin{eqnarray*}
s_p^2&=&\frac{s_X^2(n_X-1)+s_Y^2(n_Y-1)}{n_X+n_Y-2}.\\
S.E.(\bar{X}-\bar{Y})&=&\sqrt{s_p^2\left(\frac{1}{n_X}+\frac{1}{n_Y}\right)}.\\
\end{eqnarray*}
\end{frame}


%-------------------------------------------------------------------------------------------%
\begin{frame}
\frametitle{Example 2: Difference in Means (a) }
\begin{itemize}
\item For a random sample of 10 light bulbs for a particular brand, the mean bulb life is 4,000 hr with a sample standard deviation of 200 hours.
\item For another brand of bulbs, a random sample of 8 has a sample mean lifetime of 4,300 hours
and a sample standard deviation of 250 hours. \item Test the hypothesis that there is no difference between the
mean operating life of the two brands of bulbs, using the 5 percent level of significance
\end{itemize}
\end{frame}

%-------------------------------------------------------------------------------------------%

\begin{frame}
\frametitle{Example 2: Difference in Means (b) }
\begin{itemize}\item $n_1 = 10$ and $n_2 = 8$.
\item $\bar{x}_1 = 4000$, $\bar{x}_2 = 4,300 $ , therefore  $\bar{x}_1 - \bar{x}_2 = -300$ hours
\item $s_1  = 200$, $s_2 = 250$ hours.
\item Small sample - Degrees of freedom $n_1 + n_2 - 2 = 10 + 8 - 2 = 16$
\end{itemize}\end{frame}
%-------------------------------------------------------------------------------------------%
\begin{frame}
\frametitle{Example 2: Difference in Means (c) }
\textbf{Pooled variance estimate}
\[ s^2_p = {(n_1 - 1)s^2_1  + (n_2 - 1)s^2_ 2\over n_1 + n_2 - 2 } = {(9 \times 200^2 ) +( 7 \times 250^2) \over 16 }  \]
\[ s^2_p  = 49843.75 \]
\end{frame}

%-------------------------------------------------------------------------------------------%
\begin{frame}
\frametitle{Example 2: Difference in Means (d) }
\textbf{Computing the Standard Error}
\[ S.E(x_1 - x_2) = \sqrt{s^2_p \left({1\over n_1}+{1\over n_2} \right)}\]

\[ S.E(x_1 - x_2) = \sqrt{49843.75 \left({1\over 10}+{1\over 8} \right)}\]

\[ S.E(x_1 - x_2) = \sqrt{11214.84} = 105.9\]

\end{frame}

%-------------------------------------------------------------------------------------------%
\begin{frame}
\frametitle{Example 2: Difference in Means (e) }
\textbf{Test Statistic and Critical Value}\\
\begin{itemize}
\item The Test Statistic is \[ TS  = {(-300) - 0 \over 105.9}  = -2.83 \]
\item The Critical Value is determined with $\alpha = 0.05$, $k=2$, $df = 16 $
\item $CV = 2.120$
\item We can now apply the decision rule : Is the absolute value of the Test Statistic greater than the Critical Value?
\item Is $2.83 > 2.12$? Yes We reject $H_0$. There is evidence of a difference in means.
\end{itemize}
\end{frame}

\end{document}
